Parsing mPFC: A Joint Meta-Analytic and Graph Theoretic Approach

### 2018-12-06 Manuscript.Rmd
Made a quick structuring change: sliding post overall

@@

# Do a mixed effects GLM (binomial) to estimate the relationship between Fiedler vec and propDMN
SC_FVvPDMN_model <- glmer(slidePropDMN ~ FiedlerVec + (1 | SubjID), family = "binomial", data = allSummaries)
SC_FVvPDMN_modelSummary <- summary(SC_FVvPDMN_model)
allSummaries$FittedVals <- fitted(SC_FVvPDMN_model)

We complemented these analyses by asking whether the magnitude of values in the Fiedler vector was associated with the stability of nodes throughout a subject's time series (*PERSONAL NOTE: It might be better to justify this from the use of this vector in statistical mechanics rather than mere curiosity, i.e. extreme FV values are given to elements at the peaks of the wave. Find a simple citation for this.*). Specifically, we examined whether Fiedler vector values could predict the proportion of DMN affiliations per node by performing a logistic mixed effects model, with subject acting as a random effect (Figure 11). The model yielded a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDMN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDMN_modelSummary$coefficients[2,2], digits = 2)`,*p*< 0.001), meaning that vertices with higher absolute Fiedler vector values were more persistent in their relationship with their corresponding community in time. These analysis show that the original pattern identified with the full dataset is temporally stable in time, and that there is potential value in thresholding the Fiedler vector as a means to capture idiosyncratic and reliable DMN vertices in relatively short fMRI sessions (i.e. less than 20 mins).

>>>>

# Do a mixed effects GLM (binomial, quasi unavailable on glmer) to estimate the relationship between Fiedler vec and propDMN
SC_FVvPDMN_model <- glmer(slidePropDMN ~ FiedlerVec + (1 | SubjID), family = "binomial", data = allSummaries)
SC_FVvPDMN_modelSummary <- summary(SC_FVvPDMN_model)
allSummaries$FittedVals <- fitted(SC_FVvPDMN_model)

We complemented these analyses by asking whether the magnitude of values in the Fiedler vector was associated with the stability of nodes throughout a subject's time series (*PERSONAL NOTE: It might be better to justify this from the use of this vector in statistical mechanics rather than mere curiosity, i.e. extreme FV values are given to elements at the peaks of the wave. Find a simple citation for this.*). Specifically, we examined whether Fiedler vector values could predict the proportion of DMN affiliations per node by performing a logistic mixed effects model, with subject acting as a random effect (Figure 11). The model yielded a positive significant relationship between these features ($\beta$ = `r round(SC_FVvPDMN_modelSummary$coefficients[2,1], digits = 2)`, SE = `r round(SC_FVvPDMN_modelSummary$coefficients[2,2], digits = 2)`, *p* < 0.001), meaning that vertices with higher absolute Fiedler vector values were more persistent in their relationship with their corresponding community in time. These analysis show that the original pattern identified with the full dataset is temporally stable in time, and that there is potential value in thresholding the Fiedler vector as a means to capture idiosyncratic and reliable DMN vertices in relatively short fMRI sessions (i.e. less than 20 mins).

@@
